\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[colorlinks=true, linkcolor=black, urlcolor=black]{hyperref}
\usepackage{geometry}
% Increase left and right margins; adjust as needed
\geometry{left=2.0cm, right=2.0cm, top=1.0cm, bottom=1.0cm}
\usepackage{lmodern}

% Remove paragraph indentation and add spacing between paragraphs
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

\begin{document}

% Header with contact info (optional)
\begin{center}
    {\Large \textbf{Farhan Hossein}}\\
    (226) 750-1619 \quad $\vert$ \quad \href{mailto:farhan.hossein@gmail.com}{farhan.hossein@gmail.com} \quad $\vert$ \quad \href{https://linkedin.com/in/fhossein}{in/fhossein}
\end{center}

\vspace{1em}

\textbf{\today}

\vspace{1em}

Dear Hiring Manager,

I am writing to express my interest in the Software Engineer, Frontend position at Coinbase. With extensive hands-on experience building and refining web applications using React and Node.js, I am eager to contribute my skills to a company dedicated to transforming the financial landscape through innovative technology.

At Ford, I developed additional features and fixed bugs for the existing Amazon Alexa functionality within infotainment systems, ensuring a smoother user experience. At General Motors, I contributed to the ongoing maintenance and minor improvements of network features, including work related to telemetry data visualization. In addition, during my time at D2L, I built a React-based status page to monitor internal systems using AWS services, further honing my expertise in responsive, data-driven interfaces.

I am driven by a commitment to delivering practical, reliable solutions and thrive on tackling challenging problems. I value the opportunity to learn and grow alongside talented professionals, and I believe my experience aligns well with Coinbase's mission and fast-paced work culture.

Thank you for considering my application. I look forward to discussing how I can contribute to the continued success of Coinbase.

Sincerely,

Farhan Hossein

\end{document}
