\documentclass[a4paper,11pt]{article}  % Declare document class first

\usepackage{tgtermes}  % Closer to actual Times New Roman
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage[colorlinks=true, linkcolor=black, urlcolor=black]{hyperref}

\hyphenpenalty=10000
\exhyphenpenalty=10000

\definecolor{darkblue}{RGB}{0,0,139}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}

\titleformat{\section}{\large\scshape}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\begin{document}

\begin{center}
    {\Huge\textbf{Farhan Hossein}}
\end{center}
\vspace{-4mm}

\begin{center}
    \small{
    (226) 750-1619 | \href{mailto:farhan.hossein@gmail.com}{farhan.hossein@gmail.com} | 
    \href{https://linkedin.com/in/fhossein}{in/fhossein/}
    }
\end{center}
\vspace{-6mm}

\section{Summary}
\noindent Software developer with hands-on experience in full-stack web development (React, Node.js), cloud infrastructure, and embedded systems. Quick to pick up new technologies and adapt to evolving technical challenges.

\section{Experience}

\subsection*{Software Development Intern, Ford Motor Company}
\textit{Waterloo, Ontario} \hfill May 2024 - August 2024
\begin{itemize}
    \item Improved in-car user interactions by contributing to the development of Amazon Alexa voice integration features in Ford’s infotainment systems.
    \item Diagnosed and resolved software issues across modules by analyzing logs and testing system behavior in real-time environments.
    \item Collaborated with cross-functional teams to validate feature performance and ensure compliance with integration standards.
\end{itemize}


\subsection*{Software Developer, General Motors}
\textit{Markham, Ontario} \hfill May 2023 - April 2024
\begin{itemize}
    \item Developed network features for GM’s infotainment systems, enhancing user experience and connectivity.
    \item Created flowcharts to clarify internal network stack architecture and code libraries including QNX and Android.
    \item Designed a web application using Node.js and React to process vehicle telemetry data and generate customized charts.
\end{itemize}

\subsection*{Software Development Intern, General Motors}
\textit{Markham, Ontario} \hfill May 2022 - December 2022
\begin{itemize}
    \item Developed network features for GM’s infotainment systems, enhancing user experience and connectivity.
    \item Gained experience with vehicle diagnostic protocols and products (OBDII, Neo-Fire, Vehicle Spy).
    \item Developed a gamified safe driving app during a GM Hackathon to promote safe driving habits.
    \item Applied machine learning models using PyTorch on a GPU server to predict software defects.
\end{itemize}

\subsection*{Site Reliability Engineer, Desire 2 Learn}
\textit{Kitchener, Ontario} \hfill January 2022 - April 2022
\begin{itemize}
    \item Contributed to the development and maintenance of D2L’s internal monitoring systems.
    \item Developed a real-time status page from scratch using React and AWS services to improve internal system visibility.
\end{itemize}

\subsection*{Product Specialist, Cloud Delivery, OpenText Corporation}
\textit{Waterloo, Ontario} \hfill March 2016 - June 2018
\begin{itemize}
    \item Maintained internally hosted enterprise applications to ensure reliability and optimal performance.
    \item Collaborated with consulting, support, and engineering teams to resolve operational issues.
    \item Automated monitoring of enterprise app components through custom scripting.
\end{itemize}

\subsection*{Technical Analyst, OpenText Corporation}
\textit{Waterloo, Ontario} \hfill July 2014 - March 2016
\begin{itemize}
    \item Served as the first point of contact for technical inquiries regarding the Media Management product and its integration.
    \item Contributed to the product knowledge base and collaborated on cross-team issues to resolve software defects and implement feature requests.
\end{itemize}

\subsection*{Technical Support Representative / Software Tester, NeoTerra Systems}
\textit{Orangeville, Ontario} \hfill December 2013 - June 2014
\begin{itemize}
    \item Provided remote support for existing systems and new deployments.
    \item Participated in new product development testing.  
    \item Maintained the company website and version tracking functionality on the company website, enhancing deployment accuracy.
\end{itemize}

\subsection*{Wireless Network Technician, Megawire Inc}
\textit{Breslau, Ontario} \hfill May 2013 - December 2013
\begin{itemize}
    \item Deployed wireless network infrastructure to expand coverage and improve redundancy. 
    \item Configured high-frequency transceivers and network switches/routers as required.
\end{itemize}

\subsection*{Bluetooth Compliance Associate, BlackBerry}
\textit{Waterloo, Ontario} \hfill May 2010 - August 2011
\begin{itemize}
    \item Bluetooth compliance testing was conducted to maintain the quality and standards of the implementation.
    \item Automated test case execution and log collection by developing custom scripts to increase efficiency and accuracy.
\end{itemize}

\section{Education}

\subsection*{University of Waterloo}
\textit{Master of Engineering - Computer and Electrical Engineering} \hfill Graduated April 2025

\subsection*{McMaster University}
\textit{Bachelor of Technology - Software Engineering Technology (Co-op)} \hfill Graduated 2023

\subsection*{Conestoga College}
\textit{Advanced Diploma - Electronics Engineering Technology (Co-op)} \hfill Graduated 2012

\section{Skills}

\begin{itemize}
    \item \textbf{Web Development:} React, Django, Node.js
    \item \textbf{Cloud Deployment:} AWS, Microsoft Azure
    \item \textbf{Embedded Systems:} Android Open Source Project, QNX, Arduino
    \item \textbf{Wireless Technologies:} Bluetooth, Wi-Fi, and Mobile
    \item \textbf{Software Development:} Java, Python, C++, JavaScript, SQL
\end{itemize}

\end{document}
